---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# interpretproteinidentification

<!-- badges: start -->
<!-- badges: end -->

The goal of interpretproteinidentification is to improve the interpretbility of protein inference

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>. -->

<!-- You can also embed plots, for example: -->

```{r pressure, echo = FALSE}
#plot(pressure)
```

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN. -->

## Description
The purpose of this package is to visualize the connection between peptide identified from mass spectrometry, and the protein that the peptide can map to, and and to improve interpertability of a proteome. This package is not trying to show a plot that visualizes the performance of protein inference, nor is it trying to visualize the connection between mass spectrometry spectra and peptides. The main reason why is the interesting is because one peptide sequence can map to multiple proteins sequence (because or else if one peptide can only map to one protein, visualization of this kind would not provide much information), even though there can be one protein that a peptide map to that is most probable, so this means that this package can show the what conclusion (protein) has been drawn (inferred) given the evidences (peptide), and what other conclusion could have been drawn (other protein that could possibly be inferred). In theory, cytoscape can do this, (since it is a visualizer for any network), but file reading (idXML is not an supported file format) and processing (having to click many thing in the graphical user interface, or run a few command in the command line interface) may be an issue, there is a possibly that directly maybe more time-consuming (in non-automated parts).
The R version is 4.0.2 and the platform used to develop this package is Mac. 

## Installation

You can install the development version of interpretproteinidentification from [GitHub](https://github.com/) with:
```{r, message=FALSE, results='hide', warning=FALSE}
require("devtools")
devtools::install_github("kairenchen721/interpretproteinidentification", build_vignettes = TRUE)
library("interpretproteinidentification")
```
  
To run the shinyApp:
         Under construction

## Overview
```{r}
ls("package:interpretproteinidentification")
data(package = "interpretproteinidentification")
```
interpretproteinidentification contains 4 functions to visualize protein inference. The generateBipartiteGraph function generate the graph. The displayComponent allows the user to choose a component of the graph to display. selectProtein is a function that draw a sub-graph consisting of the selected protein/peptide and all its adjacent vertices. The runinterpretproteinidentification is the function that launches the shiny app for this package. (not yet implemented) The package also contains a sample idXML data. Refer to package vignettes (that will be here in the future) for more details.
```{r, eval=FALSE}
browseVignettes("TestingPackage")
```

  
## Contributions
The author of this package is Kai Ren Chen. The *generateBipartiteGraph* function make use of load function from `pyopenms` python package to read idXML files, and uses `igraph` R package to draw the graph, simplify the graph, and decompose the graph into components. displayComponents also uses the `igraph` R package to draw a component. selectProtein uses the `igraph` R package to search for relevant vertices (those connected to the selected protein/peptide), induce a sub-graph, then plot it. The data set BSA1_OMSSA.idXML is obtained from the OpenMS github. 

## Bugs to fix/Feature to implement
1. Examples in roxygen documentation fails (probably have to do with reticulate)
1. test_check fails (testing in r cmd check) despite devtools::test() works maybe I am not sure if it has something to do with getwd()
1. How do I compare edges in an igraph object?, it seems to be unsupported
1. Get data into the package and write its documentation 1.	Change plot to include inferred protein information
1. In select protein displaying protein sequence, color code peptide and protein sequence, add gene ontology labels
1. Implemented search for annotations, maybe use match
1. Consider using cytoscape	http://cytoscape.org/RCy3/articles/Cytoscape-and-iGraph.html
1. somehow, building the vignette is killed when it reach one of the functions, I suspect it because I am using reticulate 



## References

A reference for igraph
and pyopenms
also openms
also cytoscape
and all the package that this depends on 
  
## Acknowledgements
This package was developed as part of an assessment for 2021 BCB410H: Applied Bioinformatics, University of Toronto, Toronto, CANADA.


