---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# interpretproteinidentification

<!-- badges: start -->
<!-- badges: end -->

The goal of interpretproteinidentification is to ...

## Installation

You can install the development version of interpretproteinidentification from [GitHub](https://github.com/) with:

``` {r}
require("devtools")
devtools::install_github("kairenchen721/interpretproteinidentification")
```

## Example

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>. -->

<!-- You can also embed plots, for example: -->

```{r pressure, echo = FALSE}
#plot(pressure)
```

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN. -->

## Description

## Installation

To download the package:
```{r}
require("devtools")
devtools::install_github("kairenchen721/interpretproteinidentification", build_vignettes = TRUE)
library("interpretproteinidentification")
```
  
To run the shinyApp:
         Under construction

## Overview
```{r}
ls("package:interpretproteinidentification")
data(package = "interpretproteinidentification")
```

  
## Contributions
The author of this package is Kai Ren Chen. The *generateBipartiteGraph* function make use of load function from `pyopenms` python package to read idXML files, and uses `igraph` R package to draw the graph, simplify the graph, and decompose the graph into components. displayComponents also uses the `igraph` R package to draw a component. selectProtein uses the `igraph` R package to search for relevant vertices (those connected to the selected protein/peptide), induce a sub-graph, then plot it

## References

A reference for igraph
and pyopenms
  
## Acknowledgements
This package was developed as part of an assessment for 2021 BCB410H: Applied Bioinformatics, University of Toronto, Toronto, CANADA.


